\RequirePackage{etex}
\documentclass{ExpressiveResume}

% ----- Resume -----
\begin{document}

% ----- Name + Contact Information -----
\resumeheader[
    firstname=Eduardo Alejandro Aviles Jimenez,
    email=eduardo.avilesj@gmail.com,
    phone=3996-5277,
    linkedin=eduardoavilesj,
    github=steelcolosus,
    city=Zone 10,
    state=Guatemala,
    % qrcode=./images/qr.png,
    fixobjectivespacing=true
]
\begin{flushleft}
    Full-Stack Software Engineer with expertise in front-end, back-end, and Machine Learning technologies.
    Passionate about leveraging ML DevOps and CI/CD pipelines to drive innovation and efficiency. 
    Proven track record of developing AI-driven solutions that align with business goals. 
    Creative problem-solver excelling in collaborative and cross-functional environments.
\end{flushleft}

% ----- Education -----
\section{Education}

\experience
{}
{Systems Engineering}
{Jan 2005}{Sept 2011}
{
    \noindent Universidad De San Carlos De Guatemala 
}
\vspace{8pt}

% ----- Work Experience -----
\section{Work Experience}

\experience
{Machine Learning Engineer}
{LoanPro}
{Jun 2022}{Present}
{
    \achievement{
        Implemented a Loan Creation Monitor, cluster user behavior, and identify anomalies, 
        improving tenant targeting.
    }
    \achievement{
    Developed an anomaly detection system that reduced tenant noise data by 25\%, 
    filtering irrelevant events allowing the business to focus on critical insights.
    }
    \achievement{
        Created per-tenant smart threshold calculation, considering data distribution, 
        multiple modes, skewness, and kurtosis, optimizing sensitivity for better decision-making.
    }
    \achievement{
        Built automated model workflows with continuous training (CT) and model validation 
        to monitor online model performance, preventing model degradation.
    }
    \achievement{
        Developed a custom data pipeline for training and inference, 
        using ECS and Fargate for scalability and reliability.
    }
    \achievement{
        Implemented a custom LLM AI  assistant to summarize and analyze loan data and provide insights and recommendations,
    }
}
\experience
{Senior Software Engineer}
{BairesDev - HipTrain}
{Aug 2021}{Jun 2022}
{
    \achievement{
        Led infrastructure, architecture, and CI/CD pipelines for back-end and front-end solutions, 
        improving deployment times by 30\%.
    }
    \achievement{
        Developed scheduling and reservation core system for training classes, 
        improving schedulingby 80\%.
    }
    \achievement{
        Built custom generic calendar invite logic for scheduling, improving integration and user convenience.
    }
    \achievement{
        Implemented a chatbot using Amazon Lex, which automated 40\% 
        of customer inquiries and improved user interaction efficiency.
    }
    \achievement{
        Led and managed back-end and infrastructure projects, 
        ensuring scalable architecture and seamless integration with existing systems.
    }
}
\experience
{BI/ML Developer}
{LogMeIn}
{Apr 2016}{Dec 2021}
{
    \achievement{
        Developed infrastructure and architecture of core internal tools for data integration and ETL with multiple data sources, improving data processing capabilities.
    }
    \achievement{
        Built microservices to support custom ETL solutions, enhancing scalability and reliability.
    }
    \achievement{
        Implemented machine learning algorithms for internal product enhancements, leading to a 20\% increase in prediction accuracy.
    }
    \achievement{
        Developed a Twitter sentiment analysis tool for live tweet extraction and data streaming, which provided valuable insights for marketing and customer service teams.
    }
}
\experience
{Senior Software Developer}
{SSNAPP (Social Media Gateways)}
{Sep 2014}{Apr 2016}
{
    \achievement{
        Led and managed the transition from monolithic architecture to microservices using Netflix OSS, increasing system scalability by 50\% and reducing downtime during peak usage by 20%
    }
    \achievement{
        Led a team of engineers to optimize back-end infrastructure and implement cutting-edge AWS solutions, reducing infrastructure costs by 30\%.
    }
}
\vspace{8pt}
% ----- Skills -----
\section{Skills}
\begin{itemize}
    \item \textbf{Languages:} Java, Python, TypeScript, JavaScript
    \item \textbf{Libs/Frameworks:} Node.js, React, SolidJS, SolidStart, NestJS, Spring Boot, FastAPI, Django, Flask, Nameko
    \item \textbf{Machine Learning:} Scikit-Learn, TensorFlow,Keras, MLFlow, Pandas, DVC, Weights\& Biases, LlamaIndex
    \item \textbf{Cloud and DevOps:} AWS , Docker, Kubernetes, Terraform, Jenkins, CloudFormation, Ansible, GitHub Actions, Heroku
    \item \textbf{Databases:} PostgreSQL, Redis, RethinkDB, DynamoDB, Redshift
    \item \textbf{Other Tools:} Git, RabbitMQ, Netflix OSS
\end{itemize}

\pagebreak
% ------ Certifications -----
\section{Awards and Certificates}

\experience
{First Place}
{Hackathon/LoanPro}
{}{Apr 2024}
{
    \achievement{
        Loan monitoring system that utilized clustering and anomaly detection techniques to improve tenant targeting.
    }
}

\experience
{First Place}
{Hackathon/LogMeIn}
{}{Jul 2018}
{
    \achievement{
        Created an LSTM-based neural network to predict customer churn, 
        leveraging advanced recurrent neural network architectures to solve critical business problems related to customer retention.
        Also voted as developers' choice.
    }
}
\experience
{\certificate{Machine Learning DevOps Engineer}{https://www.udacity.com/certificate/e/f46ae562-cec7-11ed-b982-8f5005d0f612}}
{Nano Degree}
{Jan 2022}{Apr 2022}
{
    \achievement{
        Implement production-ready machine learning pipelines, automate data workflows with \tech{CI/CD}, use tools like \tech{FastAPI}, \tech{MLFlow}, \tech{Weights\&Biases}, and track model performance to prevent model degradation.
    }
}
\experience
{Cloud DevOps Engineer}
{Nano Degree}
{Jul 2019}{Aug 2020}
{
    \achievement{
        Deploy and maintain infrastructure as code (IaC) securely using \tech{CloudFormation} and \tech{Ansible}, create \tech{CI/CD} pipelines with \tech{Jenkins}, and operationalize scalable microservices with \tech{Kubernetes}.
    }
}
\experience
{Artificial Intelligence Nanodegree}
{Nano Degree}
{Jan 2018}{Jul 2018}
{
    \achievement{
        AI algorithms, search optimization, planning, and pattern recognition.
    }
}
\experience
{\certificate{Deep Learning Nanodegree}{https://www.udacity.com/certificate/e/67cab9d0-b612-11e7-b918-cbf0cf6d0985}}
{Nano Degree}
{Jul 2017}{Aug 2017}
{
    \achievement{         
        Built and deployed models for image classification, sentiment analysis, and face generation,
        using neural networks, convolutional neural networks (CNNs), recurrent neural networks (RNNs), 
        and generative adversarial networks (GANs).
    }
}
\vspace{8pt}

% ----- Technical Projects -----
\section{Technical Projects}

\experience
{\faIcon{lock} Loan Monitoring System}
{LoanPro}
{Jan 2024}{Present}
{
    \achievement{
    Designed and deployed a system to monitor loan creation, 
    cluster user behavior, and identify anomalies, using \tech{MLFlow}, \tech{Python}, \tech{Pandas}, and \tech{Scikit-learn}. Structured data pipeline for Training and Inference with \tech{ECS} and \tech{Fargate} for scalability and reliability.
    }
}
\experience
{\faIcon{lock} Sentiment Analysis on Twitter}
{LogMeIn}
{Jan 2024}{Present}
{
    \achievement{
        Created a real-time sentiment analysis tool for social media, allowing for better-informed marketing campaigns and customer service responses.
    }
}
\experience
{\repository{Predict Customer Churn}{https://github.com/steelcolosus/ml-devops-predict-customer-churn}}
{Personal}
{Jan 2024}{Apr 2024}
{
    \achievement{
        Implemented a Python package to predict customer churn, 
        adhering to PEP8 standards, and incorporating best practices for modularity, documentation, and testing.
    }
}
\experience
{\repository{ML Pipeline for Rental Price Prediction}{https://github.com/steelcolosus/ml-devops-build-ml-pipeline-for-short-term-rental-prices}}
{Personal}
{Jan 2024}{Apr 2024}
{
    \achievement{
        Developed an end-to-end machine learning pipeline for short-term rental price prediction in NYC, 
        including data fetching, validation, training, and deployment, automating retraining on a weekly basis.
    }
}
\experience
{\repository{Dynamic Risk Assessment System}{https://github.com/steelcolosus/ML_DevOps_NG/tree/master/project_dynamic_risk_assesment}}
{Personal}
{Jan 2024}{Apr 2024}
{
    \achievement{
        Set up automated processes to ingest data, score, re-train, and re-deploy ML models for risk assessment, ensuring models remained accurate and up-to-date.
    }
}
\experience
{\repository{Face Generation using GANs}{https://github.com/steelcolosus/face.generation}}
{Personal}
{Jan 2017}{Apr 20217}
{
    \achievement{
        Built and trained a custom GAN architecture on the CelebA dataset to generate realistic human faces, utilizing advanced techniques like DCGAN, CycleGAN, and StyleGAN.
    }
}
\vspace{8pt}


% ----- Technical Projects -----
\section{Speaking Engagements}

\experience
{Neural Network from scratch}
{FaceBook dev Circles, Guatemala}
{}{March 2019}
{
    \achievement{
        Discussed how to implement a neural network without external ML libraries, showcasing fundamental AI concepts with raw Python.
    }
}
\experience
{RNNs and Sequence to Sequence Model}
{FaceBook dev Circles, Guatemala}
{}{Oct 2018}
{
    \achievement{
        How to implement a custom RNN-based model to generate fake threads of posts and comments, trained on a dataset from the "Velocidad Maxima" website.
    }
}
\experience
{Neural Machine Translation}
{Mayan Linguistic Conference, Guatemala}
{}{Jul 2018}
{
    \achievement{
        Presented on the evolution of text translation and the potential use of neural translation models to translate Mayan dialects, exploring language preservation techniques.
    }
}
\experience
{Generative Adversarial Networks ( GAN )}
{Google IO Extended, Guatemala}
{}{May 2018}
{
    \achievement{
        Delivered a keynote on the implementation of Generative Adversarial Networks (GANs) for generating fake facial images, demonstrating the versatility of GANs in various applications.
    }
}

\end{document}
